Younger, Unmarried, Childless, and Less Happy Americans Use the Internet the Most

### 2023-03-16 outputs/paper/paper.qmd
add google forms link to the appendix
adjusted the graph labels for childs and marital

# Bar graph showing relationship between number of children and marital status
cleaned_2016gss_data |>
  ggplot(mapping = aes(x = childs, fill = marital)) + 
  geom_bar(position = "dodge2")
  labs(x = "Number of Children", y = "Number of Respondents", fill="Marital Status")
```

@@

>>>>

# Bar graph showing relationship between number of children and marital status
cleaned_2016gss_data |>
  ggplot(mapping = aes(x = childs, fill = marital)) + 
  geom_bar(position = "dodge2") +
  labs(x = "Number of Children", y = "Number of Respondents", fill="Marital Status")
```

@@

Please find our supplementary survey to the GSS 2016 questionnaire at the following link: https://docs.google.com/forms/d/e/1FAIpQLSe0H6LMKnAehmWwiag4u4cBW27ttiRh_kY1SfmOc7pQWlNrrQ/viewform?usp=sf_link
